### 2018-05-18 manuscript.rmd
updated text and S10 figure re: IQTree runs/model selection

To test the robustness of the results to model selection, we also used IQTree to implement other ML analyses using different models of substitution [@doi:10.1093/molbev/msu300; @doi:10.1093/molbev/msx281].  We also evaluated effects of method (ML vs. BI), model, and program by running a fixed-state WAG+$\Gamma$ model in Phylobayes (Fig. S12) and an ML approximation of CAT models in IQTree (Fig. S10).

@@

![\label{gene-occupancy}80% gene occupancy matrix for 41 species across 1,423 genes. Genes and species are sorted by sampling, the best sampled shown in the upper left.](supplementary_info/Supplementary_Figure1.png)

@@

```{r supplementary-trees, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Phylogenies obtained using different models of evolution. Unlabeled nodes have support >0.99. A. JTT + Empirically counted frequencies from alignment + FreeRate model with 7 categories (best model fit). Likelihood:-8113694.922; AIC:16227609.9565 .  B. GTR + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. Likelihood: -8133157.335; AIC:16266530.7277. C. WAG + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. Likelihood: -8156043.772; AIC score: 16312303.6120 "}

>>>>

To test the robustness of the results to model selection, we also used IQTree to implement other ML analyses using different models of substitution (GTR, JTT)  [@doi:10.1093/molbev/msu300; @doi:10.1093/molbev/msx281].  We used ModelFinder to assess model fit [@kalyaanamoorthy2017modelfinder].We also evaluated effects of method (ML vs. BI), model, and program by running a fixed-state WAG+$\Gamma$ model in Phylobayes (Fig. S12).

@@

![\label{gene-occupancy}80% gene occupancy matrix for 41 species across 1,423 genes.](supplementary_info/Supplementary_Figure1.png)

@@

```{r supplementary-trees, echo=FALSE, message=FALSE, warning=FALSE, verbose= FALSE, fig.width=6.5, fig.height=7, fig.cap= "Phylogenies obtained using different models of evolution in IQTree to test the robustness of the results to model selection. We used ModelFinder [@kalyaanamoorthy2017modelfinder] to assess model fit and to test the robustness of the results to model selection, we also used the WAG and GTR model. Unlabeled nodes have support >0.99. A. JTT + Empirically counted frequencies from alignment + FreeRate model with 7 categories (best model fit). Likelihood:-8113694.922; AIC:16227609.9565 .  B. GTR + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. Likelihood: -8133157.335; AIC:16266530.7277. C. WAG + Optimized base frequencies by maximum-likelihood + Free rate model with 6 categories. Likelihood: -8156043.772; AIC score: 16312303.6120 "}
